### 2013-05-30 inst/examples/BUGS/parametric-vs-nonparametric.Rmd
errors on Myers MCMC and Ricker optimization...

```{r plotting-options, cache=FALSE, message=FALSE, warning=FALSE, include=FALSE}
setwd("~/Documents/code/nonparametric-bayes/inst/examples/BUGS/")
#library(knitcitations)
library(ggplot2) 
library(nonparametricbayes) 
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=TRUE, comment=NA, fig.path="figure/parametric-"
               fig.width=6, fig.height=4, cache.path="parametric-vs-nonparametric/", verbose=TRUE)
#opts_knit$set(upload.fun = socialR::flickr.url)
theme_set(theme_bw(base_size=12))
theme_update(panel.background = element_rect(fill = "transparent", colour = NA),
             plot.background = element_rect(fill = "transparent", colour = NA))
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
               "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

@@

```{r jags-setup}
y <- obs$x[-1] 
N <- length(y);
jags.data <- list("N"=N,"y"=y)
n.chains <- 6
n.iter <- 5e5
n.burnin <- floor(10000)
n.thin <- max(1, floor(n.chains * (n.iter - n.burnin)/1000))
n.update <- 10
```

@@

```{r allen-mcmc, dependson=c("allen-model", "allen-pars", "jags-setup")}
jags.params=c("K","logr0","logtheta","stdQ", "stdR") # be sensible about the order here

@@

```{r ricker-mcmc, dependson="ricker-model"}
# Uniform priors on standard deviation terms
jags.params=c("K","logr0", "stdQ", "stdR")
jags.inits <- function(){
  list("K"= 10 * rlnorm(1,0,.5),
       "logr0" = log( rlnorm(1,0,.5) ),
       "stdQ"= 0.2 * rlnorm(1,0,.2),
       "stdR"= 1e-5 * rlnorm(1,0,.1),
       "x"=y,
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}
set.seed(12345) 
ricker_jags <- do.call(jags.parallel, 
                       list(data=jags.data, inits=jags.inits, 
                            jags.params, n.chains=n.chains, 
                            n.iter=n.iter, n.thin=n.thin, n.burnin=n.burnin,
                            model.file="ricker.bugs"))
recompile(ricker_jags)
ricker_jags <- do.call(autojags, 
                       list(object=ricker_jags, n.update=n.update, n.iter=n.iter, 
                            n.thin = n.thin, progress.bar="none"))
```

@@

```{r myers-mcmc, dependson="myers-model"}
jags.params=c("logr0", "logtheta", "logK", "stdQ", "stdR")
jags.inits <- function(){
  list("logr0" = log(rlnorm(1,0,.5)), 
       "logK" = log(10 * rlnorm(1,0,.2)),
       "logtheta" = log( 2 * rlnorm(1,0,.2)),  
       "stdQ"= 0.2 * rlnorm(1,0,.1),
       "stdR"= 1e-5 * rlnorm(1,0,.1),
       "x"=y,
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}
set.seed(12345)
myers_jags <- do.call(jags.parallel, 
                      list(data=jags.data, inits=jags.inits, jags.params, 
                           n.chains=n.chains, n.iter=n.iter, n.thin=n.thin,
                           n.burnin=n.burnin, model.file="myers.bugs")
myers_jags <- do.call(autojags, 
                      list(object=myers_jags, n.update=n.update, n.iter=n.iter, 
                           n.thin = n.thin, progress.bar="none"))
```

>>>>

```{r plotting-options, cache=FALSE, message=FALSE, warning=FALSE, include=FALSE}
source("~/.knitr_defaults.R")
#opts_knit$set(upload.fun = socialR::flickr.url)
library(knitcitations)
library(nonparametricbayes) 
```

@@

```{r jags-setup}
y <- obs$x[-1] 
N <- length(y);
jags.data <- list("N","y")
n.chains <- 6
n.iter <- 5e5
n.burnin <- floor(10000)
n.thin <- max(1, floor(n.chains * (n.iter - n.burnin)/1000))
n.update <- 10
```

@@

```{r allen-mcmc, dependson=c("allen-model", "allen-pars", "jags-setup"), results="hide"}
jags.params=c("K","logr0","logtheta","stdQ", "stdR") # be sensible about the order here

@@

```{r ricker-mcmc, dependson="ricker-model", results="hide"}
# Uniform priors on standard deviation terms
jags.params=c("K","logr0", "stdQ", "stdR")
jags.inits <- function(){
  list("K"= 10 * rlnorm(1,0,.5),
       "logr0" = log( rlnorm(1,0,.5) ),
       "stdQ"= 0.2 * rlnorm(1,0,.2),
       "stdR"= 1e-5 * rlnorm(1,0,.1),
       "x"=y,
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}
set.seed(12345) 
ricker_jags <- do.call(jags.parallel, 
                       list(data=jags.data, inits=jags.inits, 
                            jags.params, n.chains=n.chains, 
                            n.iter=n.iter, n.thin=n.thin, n.burnin=n.burnin,
                            model.file="ricker.bugs"))
recompile(ricker_jags)
ricker_jags <- do.call(autojags, 
                       list(object=ricker_jags, n.update=n.update, n.iter=n.iter, 
                            n.thin = n.thin))
```

@@

```{r myers-mcmc, dependson="myers-model", results="hide"}
jags.params=c("logr0", "logtheta", "logK", "stdQ", "stdR")
jags.inits <- function(){
  list("logr0" 		= log(rlnorm(1, 0, .5)), 
       "logK" 		= log(10 * rlnorm(1, 1, .2)),
       "logtheta" = log(2 * rnorm(1, 1, .2)),  
       "stdQ"			= 0.2  * rlnorm(1, 0, .1),
       "stdR"			= 1e-5 * rlnorm(1, 0, .1),
       "x" 				= y,
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}
set.seed(12345)
myers_jags <- do.call(jags.parallel, 
                      list(data=jags.data, inits=jags.inits, jags.params, 
                           n.chains=n.chains, n.iter=n.iter, n.thin=n.thin,
                           n.burnin=n.burnin, model.file="myers.bugs"))
recompile(myers_jags)
myers_jags <- do.call(autojags, 
                      list(object=myers_jags, n.update=n.update, n.iter=n.iter, 
                           n.thin = n.thin))
```
